NumPy---Array Computation for Python

### 2020-01-09 body.tex
Typo

% S TODO: the first sentence below could flow a bit better
Around 200, the Space Telescope Science Institute (STScI) software group wrote
a re-implementation of much of Numeric, called NumArray, to support their
need to work on large memory-mapped arrays and arrays of mixed data type
records \cite{STScI-slither}.
This briefly caused the Numeric and NumArray communities to diverge, until 2005,
when Travis Oliphant embarked upon a major rewrite that aimed to be a ``best of
both worlds'' unification of Numeric and NumArray \cite{oliphant2006guide}.
This merger resulted in NumPy.

>>>>

% S TODO: the first sentence below could flow a bit better
Around 2000, the Space Telescope Science Institute (STScI) software group wrote
a re-implementation of much of Numeric, called NumArray, to support their
need to work on large memory-mapped arrays and arrays of mixed data type
records \cite{STScI-slither}.
This briefly caused the Numeric and NumArray communities to diverge, until 2005,
when Travis Oliphant embarked upon a major rewrite that aimed to be a ``best of
both worlds'' unification of Numeric and NumArray \cite{oliphant2006guide}.
This merger resulted in NumPy.
